### 2021-10-21 capstone/2021.fall/project2/project2.tex
capstone

\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{page}{1}
   \setcounter{section}{0}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf Artificial Intelligence in Fintech \hfill #4} }
       \vspace{6mm}
       \hbox to 6.28in { {\Large \hfill #1  \hfill} }
       \vspace{6mm}
       \hbox to 6.28in { {\it Instructor: #2\hfill #3} }
      \vspace{2mm}}
   }
   \end{center}
   \markboth{#1}{#1}
   \vspace*{4mm}
}

@@

\lecture{Project 2: Paper Replication Study}{Yuan Yao}{Due: 23:59 Friday 12 Nov, 2021}{21 Oct, 2021}

@@

\section{Project Requirement}

This project as a warm-up aims to explore basic techniques in machine learning.
\begin{enumerate}
\item Pick up ONE (or more if you like) favourite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to {\bf FOUR} persons per group, to work on the same problem. Each team just submit {\bf ONE} report, \emph{with a clear remark on each person's contribution}. The report can be in the format of either a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
or \emph{technical report within 8 pages}, e.g. NIPS conference style (preferred format) 
\begin{center}
\url{https://nips.cc/Conferences/2019/PaperInformation/StyleFiles}, 
\end{center}
with source codes such as Python (Jupyter) Notebooks with a detailed documentation.
\item For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{mailto:aifin.hkust@gmail.com}{aifin.hkust@gmail.com}) with a title ``\underline{MATH6010z: Project 2}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\section{Paper replication: \emph{(Re-)Imag(in)ing Price Trends}}

\subsection{Background}
We are targeting to replicate the following paper by Jingwen Jiang, Bryan Kelly and Dacheng Xiu: \\
\url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3756587}.

This paper explores convolutional neural networks that flexibly learn price patterns as images that are most predictive of future returns. The raw predictor data are images -- stock-level price charts, from which authors model the predictive association between images and future returns using a convolutional neural network (CNN). They claims that by using CNN they can automatically identify context-independent predictive patterns which can gave more accurate return predictions, translate into more profitable investment strategies and are robust to variations.

In the empirical designs, they first embeds 1D time series data in a higher dimensional space, representing it as a 2D image depicting price and volumes. Then they feed each training sample into CNN to estimate the probability of a positive subsequent return over short (5-day), medium (20-day) and long (60-day) horizons. Afterwards, they use CNN-based out-of-sample predictions as signals in a number of asset pricing analyses. Finally, they attempt to interpret the predictive patterns identified by the CNN.

\subsection{Replication studies}
In this reproduction process, we mainly focus on understanding the data preparation (how to transfer 1D time series data to 2D images representing historical market data), model design (CNN architecture design and mechanism behind it), workflow design (from training to model tuning and finally to prediction), performance evaluation and finally the interpretation part.

\begin{enumerate}
    \item \textbf{Data}

    The sample runs from 1993-2019 based on the fact that daily opening, high, low prices. In the original paper, authors construct datasets consisting three scale of horizons (5-day, 20-day, 60-day), Here we just collect the 20-day version. The total size of data is 8.6G in a zipped file (802.9MB). The download link of data is:

    \url{https://dachxiu.chicagobooth.edu/download/img_data.zip}

    or a fast access

    \url{https://www.dropbox.com/s/njehqednn8mycze/img_data.zip?dl=0}

    with iPython image processing demo in

    \url{https://dachxiu.chicagobooth.edu/download/img_demo.html}.

    We already transformed the OHLC charts into images following the same procedures introduced in the paper (Section 2). Current images have the same resolution (64 * 60) and added with moving average lines(MA) and volume bars(VB). Some example figures is shown in Figure \ref{20-day image}.

    \begin{figure}
        \centering
        \includegraphics[width=.3\textwidth]{img/1.png}
        \hspace{0.5in}
        \includegraphics[width=.3\textwidth]{img/2.png}
        \caption{Examples of 20-day Image with volume bar and moving average line}
        \label{20-day image}
    \end{figure}

    Images labels take value \textbf{1} for positive returns and \textbf{0} for non-positive returns. In addition, we use \textbf{2} to mark the NaN value. In the simplest terms, you need to complete a two-class classification problem, and use the CNN model to predict whether the trend is 'down' or 'up' for the input image. For detail of data and label file, please refer to appendix.

    \item \textbf{Architecture Design}

    Why use CNN? Since CNN impose cross-parameter restrictions that dramatically reduce parameterization and embed a number of tools that make the model resilient to deformation and re-positioning of important objects in the image. A core building block consists of three operations: convolution, activation and pooling. In the paper, for 20-day image, they build a baseline CNN architectures with 3 conv blocks and connected with a fully connected layer as a classifier head. You should refer to the design of the conv block in the original paper (including the selection of the size of the convolution kernel, the selection of the convolution method, the design of the pooling layer and the selection of the activation function, etc) Figure \ref{cnn model} shows a diagram of 20-day CNN model proposed in the paper, just for your reference.

    \begin{figure}
        \centering
        \includegraphics[width=.25\textwidth, height=0.45\textwidth]{img/cnn.png}
        \caption{Diagram of CNN model}
        \label{cnn model}
    \end{figure}

    \item \textbf{Working Flow}

    \begin{description}
    \item[Data split] First, consider dividing the entire sample into training, validation and testing samples. In the original paper, they use first seven-year sample (1993-1999) to train and validate model, in which 70\% of the sample are randomly selected for training and the remaining 30\% for validation. The remaining twenty years of data  comprise the out-of-sample test dataset. You should consider follow the same format in case better comparson with the original paper.

    \item[Loss and evaluation] You can simply treat the prediction analysis as a classification problem. In particular, the label for an image is defined as y = 1 if the subsequent return is positive and y = 0 otherwise. The training step minimizes the cross-entropy loss, which is the standard objective function for classification problem, which define as:$$L_{CE}(y,\hat{y}) = -y\log(\hat{y}) - (1-y)log(1-\hat{y})$$ where $\hat{y}$ is the prediction and $y$ is the ground truth.

    To measure the classification accuracy, a true positive (TP) (true negative (TN)) occurs when a predicted probability of greater than 50\% coincides with a positive realized return (a probability less than 50\% coincides with a negative return, respectively). False positives and negatives (FP and FN) are the complementary outcomes. We calculate classification accuracy as:$$Accuracy = (TP + TN)/(TP + TN + FP + FN)$$ For more evaluation metrics or methods, like Sharpe Ratio, please refer to the original paper.

    \item[Training process] The author adopt several ways to combat over-fitting issue and aid efficient computation. For example, they applied the Xavier initialization for weights in each layer, which guarantees faster convergence by scale the initial weights. Other techniques like dropout, batch normalization and early stopping may also improve performance. We recommend to refer to the training details mentioned in the paper 3.3 when training the baseline model.

    \end{description}

    \item \textbf{Extensions}

    \begin{itemize}
        \item For ablation studies and testing robustness, we suggest you follow what original paper mentioned in Appendix B. For example, you can perform the same sensitivity analysis of the CNN prediction model to alternate choices in model architecture (e.g. varying the number of filters in each layer or varying the number of layers, like the paper shows in Table 18)

        \item Another direction that can be used as an extension is exploring of the interpretability of the CNN model in Chapter 6 of the original paper. Though interpreting a CNN model is quite difficult due to its stacks of non-linear structures, you can imitate what the author did in Part 6.3, using a visualization method (Grad-CAM) to understand how different image examples activate the regions of the CNN to trigger `up' or `down' return predictions.

        \item What's more, we encourage you not being limited to simple binary classification task, since the label files we provided consist more meaningful attributes, containing both categorical and numerical values. For example, you can use the same 20-day horizon images to train your model to predict the return trend of different subsequent \textbf{y}-days even the detailed return values. (\textbf{y} can be 5, 20 even larger). In this way, you can prove more firmly that using CNN can automatically identity robust and transferable predictive features.
    \end{itemize}

\section{Paper replication: Empirical Asset Pricing via Machine Learning}

The fundamental goal of asset pricing is to understand the behavior of risk premiums. However, risk premium is difficult to measure: market efficiency forces return variation to be dominated by unforecastable news that obscures risk premiums. This paper predicts the expected return and identifies informative predictor variables via machine learning methods, which facilitates more reliable investigation into economic mechanisms of asset pricing. Now you are required to replicate some results of this paper based your understanding of it, and write a report about your work.

The requirements of this paper replication project are as follow:
\begin{itemize}
\item The machine learning methods used in this paper include linear regression (OLS, elastic net), dimension reduction (PLS, PCR), generalized linear models, trees (gradient boosting trees, random forest) and neural networks. Please try to replicate \textbf{at least 6 methods} of them (e.g., OLS, elastic net, PLS, PCR, random forest, neural networks, etc. Please note that if you choose OLS, OLS-3 should also be included; and if you choose neural network, NN1 to NN5 are included. Besides, robust loss function should also be considered. See details in the paper), and analyze your results specifically. Hints on parameter choice are presented in the paper.
\item Include the variable importance (section 2.3 of the paper) in your analysis. You do not need to replicate all the figures in section 2.3, but you are encouraged to investigate it carefully.
\item Note that this paper uses a `recursive performance evaluation scheme'. You are also required to evaluate your result by this method. For more details of this method, please refer to the paper and its supplementary material. The PPT presented in class about this project may also be helpful to you.
\item As you can know from the paper, the 8 macroeconomic predictors are constructed following Welch and Goyal (2008), and it is not directly included in the dataset. You should construct them by yourself.
\item The portfolio forecast part of the paper (section 2.4) is not compulsory for you to replicate.
\end{itemize}

You may access the paper and the supplementary material via: \\
\url{https://dachxiu.chicagobooth.edu/download/ML.pdf} \\
or \\
\url{https://academic.oup.com/rfs/article/33/5/2223/5758276}.  \\
Meanings of characteristics of the data are provided in the supplementary material.

The original dataset (4.05GB) can be obtained at \\ 
\url{https://dachxiu.chicagobooth.edu/download/datashare.zip}. \\
The zip file is about 1.64GB. Please be patient since it may take you about 6 hours to download the data. Another fast access can be via \\
\url{https://www.dropbox.com/s/zzgjdubvv23xkfp/datashare.zip?dl=0}

% \section{Kaggle Contest: Home Credit Default Risk}

% Many people struggle to get loans due to insufficient or non-existent credit histories. And, unfortunately, this population is often taken advantage of by untrustworthy lenders.

% Home Credit strives to broaden financial inclusion for the unbanked population by providing a positive and safe borrowing experience. In order to make sure this underserved population has a positive loan experience, Home Credit makes use of a variety of alternative data--including telco and transactional information--to predict their clients' repayment abilities.

% While Home Credit is currently using various statistical and machine learning methods to make these predictions, they're challenging Kagglers to help them unlock the full potential of their data. Doing so will ensure that clients capable of repayment are not rejected and that loans are given with a principal, maturity, and repayment calendar that will empower their clients to be successful.

% Visit the following website to join the competition.

% \url{https://www.kaggle.com/c/home-credit-default-risk/}

% {\bf Requirements}. For Kaggle contests, please register your team with name in the format of math6010z\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

@@

{\bf Deadline is \emph{11:59pm November 19, 2021}}. Submit your review in plain text to the email address (\url{aifin.hkust@gmail.com}) with title: \underline{MAFS6010Z: Project 2 Review}. Rebuttal is open afterwards.

@@

%You should put each review in a plain text separately with a title  comprising the corresponding group number (\textbf{not your own group}) and your name (e.g., \emph{\underline{rev1\_group03\_Ian\_Goodfellow.pdf}}). Submit all your reviews in a single zip file \textbf{using canvas}. Rebuttal is open afterwards.

\begin{itemize}
\item Summary of the report.
\item Describe the strengths of the report. 
\item Describe the weaknesses of the report.
\item Evaluation on Clarity and quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
\item Evaluation on Technical Quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
\item Confidence on your assessment (1-3)
(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
\end{itemize}
%
%%Then please vote your top THREE favourite reports on Doodle: 
%%\url{xxx}
%
\newpage

\section*{Rebuttal}
The rebuttal period starts from now, till \emph{11:59pm Nov 22, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.

>>>>

\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{page}{1}
   \setcounter{section}{0}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf Capstone Project for Data Science \hfill #4} }
       \vspace{6mm}
       \hbox to 6.28in { {\Large \hfill #1  \hfill} }
       \vspace{6mm}
       \hbox to 6.28in { {\it Instructor: #2\hfill #3} }
      \vspace{2mm}}
   }
   \end{center}
   \markboth{#1}{#1}
   \vspace*{4mm}
}

@@

\lecture{Project 2. Final Project with Images and Text.}{Yuan Yao}{Due: 23:59 Sunday 14 Nov, 2021}{21 Oct, 2021}

@@

\section{Mini-Project Requirement and Datasets}

This project as a warm-up aims to explore basic techniques in machine learning.
\begin{enumerate}
\item Pick up ONE (or more if you like) favourite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to {\bf TWO} persons per group, to work on the same problem. Each team just submit {\bf ONE} report, \emph{with a clear remark on each person's contribution}. The report can be in the format of either a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
or \emph{technical report within 8 pages}, e.g. NIPS conference style (preferred format) 
\begin{center}
\url{https://nips.cc/Conferences/2019/PaperInformation/StyleFiles}, 
\end{center}
with source codes such as Python (Jupyter) Notebooks with a detailed documentation.
\item For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math4995\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{datascience.hw@gmail.com}{datascience.hw@gmail.com}) with a title ``\underline{MATH4995: Project 2}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\section{Kaggle Contest: PetFinder.my - Pawpularity Contest}

\href{https://petfinder.my/}{PetFinder.my} is a Malaysia leading animal welfare platform, featuring over 180,000 animals with 54,000 happily adopted. Currently, PetFinder.my uses a basic \href{https://petfinder.my/cutenessmeter}{Cuteness Meter} to rank pet photos. It analyzes picture composition and other factors compared to the performance of thousands of pet profiles. While this basic tool is helpful, it's still in an experimental stage and the algorithm could be improved.

In this competition, you will analyze raw images and metadata to predict the \emph{Pawpularity} of pet photos. You'll train and test your model on PetFinder.my's thousands of pet profiles. Winning versions will offer accurate recommendations that will improve animal welfare. As a result, stray dogs and cats can find their ``furever" homes much faster. With a little assistance from the Kaggle community, many precious lives could be saved and more happy families created.

Visit the following website to join the competition.

\url{https://www.kaggle.com/c/petfinder-pawpularity-score}

{\bf Requirements}. For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math4995\_Zhu\_Wong.

\section{Kaggle Contest: Natural Language Processing with Disaster Tweets}

Twitter has become an important communication channel in times of emergency.
The ubiquitousness of smartphones enables people to announce an emergency they are observing in real-time. Because of this, more agencies are interested in programatically monitoring Twitter (i.e. disaster relief organizations and news agencies).

But, it is not always clear whether a person's words are actually announcing a disaster.

In this competition, you are challenged to build a machine learning model that predicts which Tweets are about real disasters and which ones are not. You will have access to a dataset of 10,000 tweets that were hand classified.

Disclaimer: The dataset for this competition contains text that may be considered \emph{profane}, \emph{vulgar}, or \emph{offensive}.

Visit the following website to join the competition.

\url{https://www.kaggle.com/c/nlp-getting-started}

{\bf Requirements}. For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math4995\_Zhu\_Wong.

\section{Datasets from Project 1}

\subsection{Kaggle Contest: Predict Survival on the Titanic}
The sinking of the Titanic is one of the most infamous shipwrecks in history.

On April 15, 1912, during her maiden voyage, the widely considered ``unsinkable" RMS Titanic sank after colliding with an iceberg. Unfortunately, there were not enough lifeboats for everyone onboard, resulting in the death of 1502 out of 2224 passengers and crew.

While there was some element of luck involved in surviving, it seems some groups of people were more likely to survive than others.

In this challenge, we ask you to build a predictive model that answers the question: ``what sorts of people were more likely to survive?" using passenger data ({\it i.e.} name, age, gender, socio-economic class, etc). Visit the following website to join the Kaggle contest:

\url{https://www.kaggle.com/c/titanic}

{\bf Requirements}. For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math4995\_Zhu\_Wong.

\subsection{Kaggle Contest: Home Credit Default Risk}

Many people struggle to get loans due to insufficient or non-existent credit histories. And, unfortunately, this population is often taken advantage of by untrustworthy lenders.

Home Credit strives to broaden financial inclusion for the unbanked population by providing a positive and safe borrowing experience. In order to make sure this underserved population has a positive loan experience, Home Credit makes use of a variety of alternative data--including telco and transactional information--to predict their clients' repayment abilities.

While Home Credit is currently using various statistical and machine learning methods to make these predictions, they're challenging Kagglers to help them unlock the full potential of their data. Doing so will ensure that clients capable of repayment are not rejected and that loans are given with a principal, maturity, and repayment calendar that will empower their clients to be successful.

Visit the following website to join the competition.

\url{https://www.kaggle.com/c/home-credit-default-risk/}

{\bf Requirements}. For Kaggle contests, please register your team with name in the format of math4995\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math4995\_Zhu\_Wong.

\section{Self Proposals}

\subsection{Workers Supervision for Construction Safety}

\url{https://yao-lab.github.io/capstone/2021.fall/project1/Project_proposal_final_TrungKien.pdf}

@@

{\bf Deadline is \emph{11:59pm Nov. 28, 2021}}. Submit all your reviews in a single zip file using \textbf{canvas}. % or to the email address  (\href{datascience.hw@gmail.com}{datascience.hw@gmail.com}) with a title ``\underline{MATH4995: Project 1 Review}". 
Rebuttal is open afterwards.

@@

%You should put each review in a plain text separately with a title  comprising the corresponding group number (\textbf{not your own group}) and your name (e.g., \emph{\underline{rev1\_group03\_Ian\_Goodfellow.pdf}}).

\begin{itemize}
\item Summary of the report.
\item Describe the strengths of the report. 
\item Describe the weaknesses of the report.
\item Evaluation on quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
%\item Evaluation on technical quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
\item Evaluation on presentation (1-5): Is the presentation clear and well organized? Are the language flow fluent and persuasive? Are the slides clear and well elaborated? Please make suggestions to improve the presentation.
\item Evaluation on creativity (1-5): Does the work propose any genuinely new ideas? Is this a work that you are eager to read and cite? Does it contain some state-of-the-art results? As a reviewer you should try to assess whether the ideas are truly new and creative. Novel combinations, adaptations or extensions of existing ideas are also valuable.
\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
\item Confidence on your assessment (1-3)
(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
\end{itemize}

%\begin{itemize}
%\item Summary of the report.
%\item Describe the strengths of the report. 
%\item Describe the weaknesses of the report.
%\item Evaluation on Clarity and quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
%\item Evaluation on Technical Quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
%\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
%\item Confidence on your assessment (1-3)
%(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
%\end{itemize}
%
%%Then please vote your top THREE favourite reports on Doodle: 
%%\url{xxx}

\section*{Rebuttal}
The rebuttal period starts from now, till \emph{11:59pm Nov. 30, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.
